Active Learning for SAT Solver Benchmarking

### 2024-04-22 paper_jar/paper.tex
Add a few To Dos
Minor adaptations to SN journal template
- remove unused packages
- some headings become separate-line instead of inline; remove full stop
  accordingly
- change bibstyle
- remove unused commands in preamble
- mark corresponding author as intended (instead of using custom symbol)
- add declarations

\documentclass{sn-jnl}

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsthm}
\usepackage[T1]{fontenc} % font encoding; recommended by LNCS template
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[misc]{ifsym} % letter symbol to mark corresponding author
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{orcidlink} % ORCID icon and link; has to be loaded after "xcolor" here, else "option clash"; class "llncs" also has command "\orcidID" (which only displays full ID), but camera-ready instructions state you should add icon and link yourself
\usepackage{tikz} % has to be loaded after "xcolor" here, else "option clash"

@@

\renewcommand\UrlFont{\color{blue}\rmfamily} % link coloring according to LNCS template

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}% 
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

@@

\title[Active Learning for SAT Solver Benchmarking]{Active Learning for SAT Solver Benchmarking}

\author{\fnm{Tobias} \sur{Fuchs}}\email{tobias.fuchs@kit.edu}
\author{\fnm{Jakob} \sur{Bach}}\email{jakob.bach@kit.edu}
\author{\fnm{Markus} \sur{Iser}}\email{markus.iser@kit.edu}

\affil{\orgname{Karlsruhe Institute of Technology}, \orgaddress{\city{Karlsruhe}, \country{Germany}}}

@@

@@

@@

\subsubsection{Static Benchmark Selection.}

@@

\subsubsection{Algorithm Configuration.}

@@

\subsubsection{Incremental Benchmark Selection.}

@@

\subsubsection{Active Learning.}

@@

\subsubsection{Runtime Transformation.}

@@

\subsubsection{Ranking Solvers.}

@@

\subsubsection{Uncertainty Sampling.}

@@

\subsubsection{Information-Gain Sampling.}

@@

\subsubsection{Wilcoxon Stopping Criterion.}

@@

\subsubsection{Ranking Stopping Criterion.}

@@

\subsubsection{Ranking.}

@@

\subsubsection{Selection.}

@@

\subsubsection{Stopping.}

@@

Table~\ref{tab:fulldataset} shows how both active-learning approaches (column \emph{AL}) compare against two static baselines:
\emph{Random} samples instances until it reaches roughly the same fraction of runtime as the AL benchmark sets.
We repeat sampling 1000 times and report average results.
\emph{Most Freq.} uses a static benchmark set consisting of those instances most frequently sampled by our active learning approach.
In particular, we consider the average sampling frequency over all solvers and Pareto-optimal active-learning approaches.

@@

@@

\subsubsection*{Acknowledgments.}

@@

%
% ---- Bibliography ----
%
\bibliographystyle{splncs04}
\bibliography{literature}

>>>>

\documentclass[sn-basic, Numbered]{sn-jnl} % may use "lineno" for line numbers
% template from https://www.springernature.com/gp/authors/campaigns/latex-author-support

\usepackage[ruled,vlined,linesnumbered,norelsize]{algorithm2e}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{tikz} % has to be loaded after "xcolor" here, else "option clash"

@@

\newtheorem{definition}{Definition} % only kind of theorems we use are definitions (well, one)

@@

\title[Active Learning for SAT Solver Benchmarking]{Active Learning for SAT Solver Benchmarking} % short and long title
%JB: not sure if we should use a new title or not; in past special issues of journal, both options (re-use conference-version title or choose new title) were used

\author*{\fnm{Tobias} \sur{Fuchs}}\email{tobias.fuchs@kit.edu}
\author{\fnm{Jakob} \sur{Bach}}\email{jakob.bach@kit.edu}
\author{\fnm{Markus} \sur{Iser}}\email{markus.iser@kit.edu}

\affil{\orgname{Karlsruhe Institute of Technology (KIT)}, \orgaddress{\city{Karlsruhe}, \country{Germany}}}

@@

% TODO: somewhere in introduction, refer to conference version ("fuchs2023active") and state what has changed in journal version
% TODO: if appropriate, extend with motivation/results regarding runtime discretization and prediction models

@@

% TODO: if appropriate, extend with related work regarding runtime discretization and prediction models

@@

\subsection{Static Benchmark Selection}

@@

\subsection{Algorithm Configuration}

@@

\subsection{Incremental Benchmark Selection}

@@

\subsection{Active Learning}

@@

\subsubsection{Runtime Transformation}

@@

\subsubsection{Ranking Solvers}

@@

\subsubsection{Uncertainty Sampling}

@@

\subsubsection{Information-Gain Sampling}

@@

\subsubsection{Wilcoxon Stopping Criterion}

@@

\subsubsection{Ranking Stopping Criterion}

@@

\subsubsection{Ranking}

@@

\subsubsection{Selection}

@@

\subsubsection{Stopping}

@@

Table~\ref{tab:fulldataset} shows how both active-learning approaches (column \emph{AL}) compare against two static baselines:
\emph{Random} samples instances until it reaches roughly the same fraction of runtime as the AL benchmark sets.
We repeat sampling 1000 times and report average results.
\emph{Most Frequent} uses a static benchmark set consisting of those instances most frequently sampled by our active learning approach.
In particular, we consider the average sampling frequency over all solvers and Pareto-optimal active-learning approaches.

@@

% TODO: if appropriate, extend with results regarding runtime discretization and prediction models

@@

\backmatter

\section*{Declarations}

\bmhead{Funding}

@@

\bmhead{Competing interests}

The authors have no competing interests to declare that are relevant to the content of this article.

\bmhead{Availability of data and materials}

All experimental data are available online at \url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking-data}.
% TODO: does this also include all the data for the newly added results?

\bmhead{Code availability}

The code is available online at \url{https://github.com/mathefuchs/al-for-sat-solver-benchmarking}.
%TODO: README in code repo should also describe how to reproduce the experiments for the newly added results (at least running the corresponding plot notebook is necessary; currently, README only refers to "anni_results.ipynb")

\bibliography{literature}
